Optimal (Multiway) Spatial Joins

### 2024-05-23 msj.tex
yufei

\begin{lemma} \label{lmm:hv:type1:cross-non-empty}
    Neither $\cross(r_a, B; H)$ nor $\cross(r_b, B; H)$ can be empty.
\end{lemma}

@@

\noindent In Appendix~\ref{app:hv}, we prove that the set $S$ computed satisfies \eqref{eqn:hv:type1:S}, as desired. If we exclude the time to compute all the $\cross(r_a, B; H)$ and $\cross(r_b, B; V)$, the running time of the above algorithm is
\myeqn{
    O(1 + |\Pi_{1:k-2}(\J_1(R_1, ..., R_{k-2}, H, V))| + |S|) \nn
}
which is $O(1 + \out)$ because of \eqref{eqn:hv:type1:S}. In what follows, we will explain how to compute all the $\cross(r_a, B; H)$ in $O(n \log n + |S|)$ time. A symmetric algorithm can be used to compute all the $\cross(r_b, B; V)$ in the same complexity. This will then allow us to conclude that Step 2 can be done in $O(n \log n + |S|)$ time.

>>>>

\begin{lemma} \label{lmm:hv:type1:cross-non-empty}
    $\cross(r_a, B; H) \ne \emptyset$ and $\cross(r_b, B; H) \ne \emptyset$.
\end{lemma}

@@

\noindent In Appendix~\ref{app:hv}, we prove that the set $S$ computed satisfies \eqref{eqn:hv:type1:S}, as desired. If we exclude the time to compute all the $\cross(r_a, B; H)$ and $\cross(r_b, B; V)$, the running time of the above algorithm is $O(1 + |S|)$, which is $O(1 + \out)$ because of \eqref{eqn:hv:type1:S}. In what follows, we will explain how to compute all the $\cross(r_a, B; H)$ in $O(n \log n + |S|)$ time. A symmetric algorithm can be used to compute all the $\cross(r_b, B; V)$ in the same complexity. This will then allow us to conclude that Step 2 can be done in $O(n \log n + |S|)$ time.
